Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-10-22 Cost_manuscript.Rmd
working on combining existing wording into new intro

  Prospectus: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it. *Effort examples here?* In neuroeconomics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015). Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013). However, people often change their attitudes towards exerting effort in everyday decisions. For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train. Understanding the sporadic attractiveness of effort exemplified above has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017). 
  Measuring the cost of effort and delay is often done by offering higher payouts for an increment of the respective demand, but flexible preferences for effort might stem from the availability of other types of demands in the same choice environment. (Kool & Botvinick, 2018). Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018). In addition, foraging tasks can allow individuals to emphasize different elements of the decision context, and rest on a rich modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
  In this study, we will test the hypothesis that preferences will vary depending on whether individuals face a single or multiple types of behavioral demands, and identify what factors drive these choices. Based on two foraging experiments and computational modeling, we will show that 1) preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
  In this study, we will behaviorally and computationally test the hypothesis that the attractiveness of a reward that requires effort or delay depends on whether rewards associated with alternative demands are available in the same context. Using a foraging paradigm will enable us to 1) assess whether people integrate the statistics of the environment to generate strategies that maximize their earnings; 2) compare how the presence of effort or delay shifts such strategies, as reflected by acceptance rates; 3) examine if acceptance rates are further altered by foraging for costs in addition to rewards; and 4) test a combination of foraging (Constantino & Daw, 2015; Stephens & Krebs, 2019; Fawcett, McNamara, & Houston, 2012) and reinforcement learning models (Sutton & Barto, 2018) to examine whether preferences for demands reflect a subjective reduction of cost or boost of value, and determine any factors besides contextual manipulations that participants consider in order to adjust their choices.

>>>>

Outline:
- Effort and delay tend to be aversive, and neuroeconhas traditionally examined them as such
- But there is a flipside of effort: it can be attractive
- One issue is that even for studies that compare across demands, they do so by quantifying discounting curves
- A less explored avenue that might get at this though is the comparison among demands
- Ecological foraging paradigms can help us with this approach, allowing for people to search for their preferred demands
- In addition, foraging rests on a rich modeling history
- We can model whether preferences for demands are due to either 1) modulating cost or embuing value relative to optimal behavior; 2) whether people attend to focal decision elements or global environmental attributes when they evaluate demanding offers
- In this study....

  Prospectus: Evaluating whether to pursue a desired outcome often requires assessing the demands required for obtaining it. In psychology and economics, demands for both time and effort have traditionally been identified as costs that detract from the net subjective value of rewards (Westbrook & Braver, 2015). Indeed, decision makers tend to prefer low-effort and immediate rewards over larger rewards that demand longer delays and higher effort (Ainslie, 1975; Hull, 1943; Kool & Botvinick, 2018; Kool, McGuire, Rosen, & Botvinick, 2010; Treadway, Buckholtz, Schwartzman, Lambert, & Zald, 2009; Westbrook, Kester, & Braver, 2013). However, people often change their attitudes towards exerting effort in everyday decisions. For example, we might choose to take the effortful route home that we normally avoid rather than waiting for a delayed train. . Understanding the sporadic attractiveness of effort exemplified above has been elusive, and presents an important research avenue (Inzlicht, Shenhav, & Olivola, 2017). (add Loewenstein 1987 and other explanatory candidates here. I think the goal will be that there are theories speculating about when demands can be valuable for a single choice decision, or in TAFC, but point out inconclusiveness. The next paragraph should say that what's missing is comparing among costs)
  A key limitation in understanding this phenomenon is that studies often compare the reduction of subjective value imposed by each type of demand, often through discounting functions that capture how much less appealing a reward becomes as a function of the amount or intensity of its associated behavior [1,3,5,8,9,14]. Although this line of work suggests that discounting functions are similar for delay and effort [8,15,16], there is ongoing debate about the shape of the discounting function across effort types [2,8,11,17,18], and discount rates do not always correlate across cost domains [9,16]. Furthermore, this approach fails to interrogate which type of demand people would select. Flexible preferences for effort might stem from the availability of other types of demands in the same choice environment (Kool & Botvinick, 2018).
  Single choice foraging paradigms provide a natural way to probe preferences among demands, by asking individuals whether the current offer outweighs what could be obtained and experienced during that time instead (Mobbs, Trimmer, Blumstein, & Dayan, 2018). In addition, foraging tasks can allow individuals to emphasize different elements of the decision context, and rest on a rich modeling history that can help to computationally capture such emphases (Stephens & Krebs, 2019).
  In this study, we will test the hypothesis that preferences will vary depending on whether individuals face a single or multiple types of behavioral demands, and identify what factors drive these choices. Based on two foraging experiments and computational modeling, we will show that 1) preferences for mental effort are stable when individuals face a single form of demand, but fade over time when other costs are also experienced; and 2) the phenomenon can be explained by a model in which preferences depend on how participants construe the amount of time a task takes, which could hypothetically be recalibrated when all tasks are interleaved.
  In this study, we will behaviorally and computationally test the hypothesis that the attractiveness of a reward that requires effort or delay depends on whether rewards associated with alternative demands are available in the same context. Using a foraging paradigm will enable us to 1) assess whether people integrate the statistics of the environment to generate strategies that maximize their earnings; 2) compare how the presence of effort or delay shifts such strategies, as reflected by acceptance rates; 3) examine if acceptance rates are further altered by foraging for costs in addition to rewards; and 4) test a combination of foraging (Constantino & Daw, 2015; Stephens & Krebs, 2019; Fawcett, McNamara, & Houston, 2012) to examine whether preferences for demands reflect a subjective reduction of cost or boost of value, and determine any factors besides contextual manipulations that participants consider in order to adjust their choices.
